### 2016-03-31 document/manuscript-plos.tex
adding a ref for software citation

In research, it is a good practice to ensure permanent and unambiguous
identifiers for citable items like articles, datasets, or biological
entities such as proteins, genes and metabolites, among others. Digital
Object Identifiers (DOIs) have been used for many years as unique and
unambiguous identifiers for enabling the citation of scientific
publications. More recently, a trend has started to produce DOIs for
other types of scientific outputs such as datasets \cite{Vizcaino:2014}
or training materials (for example \cite{Ahmadia_2015_27353}). The main
motivation behind this is to give scientists better credit for their
work \cite{NatBiotechEditorial:2009}, simultaneously enabling a better
way to cite and track it. A common issue with software is that it
normally evolves at a different speed than text published in the
scientific literature. In fact, it is common to find software having
novel features and functionalities that were not described in the
original publication. GitHub now enables the use of DOIs to cite the
code deposited, using the data archiving tool Zenodo
(\url{https://zenodo.org/}). The procedure is simple (see
\url{https://guides.GitHub.com/activities/citable-code/}) and, by default,
Zenodo creates an archive of a repository each time a new release is
created in GitHub. However, before Zenodo can issue a DOI, metadata
needs to be provided about the archived repository. Once the DOI has
been assigned, apart from using it in your CV, you can add it to
literature information resources such as Europe PubMed Central
\cite{EuropePMCConsortium:2015}. As already mentioned in the
introduction, reproducibility of scientific claims should be enabled by
openly providing the software, the datasets, and the process leading to
interpretable results that was used in a particular study. As much as possible,
publications should highlight that the code is
freely available in, for example, GitHub, and cite the DOI of the archived version
of the code that was used, together with any other
relevant information that may have been deposited. In our
experience, this openness substantially increases your chances of
getting the paper accepted for publication. On one hand, journal editors
and reviewers have the opportunity to reproduce your findings during the
manuscript review process, increasing their confidence in your results. On
the other hand, once the paper is published, your work can be reproduced
by any member of the scientific community, which can increase citations
and foster opportunities for further discussion and collaboration. Also
one must keep in mind that the availability of a public repository with
the source code does not make the software open source \emph{per se}, as
it also needs to have an appropriate license
(\url{http://opensource.org/licenses/}).

>>>>

In research, it is a good practice to ensure permanent and unambiguous
identifiers for citable items like articles, datasets, or biological
entities such as proteins, genes and metabolites, among others. Digital
Object Identifiers (DOIs) have been used for many years as unique and
unambiguous identifiers for enabling the citation of scientific
publications. More recently, a trend has started to produce DOIs for
other types of scientific outputs such as datasets \cite{Vizcaino:2014},
training materials (for example \cite{Ahmadia_2015_27353}), and software. The main
motivation behind this is to give scientists better credit for their
work \cite{NatBiotechEditorial:2009,force11-scwg}, simultaneously enabling a better
way to cite and track it. A common issue with software is that it
normally evolves at a different speed than text published in the
scientific literature. In fact, it is common to find software having
novel features and functionalities that were not described in the
original publication. GitHub now enables the use of DOIs to cite the
code deposited, using the data archiving tool Zenodo
(\url{https://zenodo.org/}). The procedure is simple (see
\url{https://guides.GitHub.com/activities/citable-code/}) and, by default,
Zenodo creates an archive of a repository each time a new release is
created in GitHub. However, before Zenodo can issue a DOI, metadata
needs to be provided about the archived repository. Once the DOI has
been assigned, apart from using it in your CV, you can add it to
literature information resources such as Europe PubMed Central
\cite{EuropePMCConsortium:2015}. As already mentioned in the
introduction, reproducibility of scientific claims should be enabled by
openly providing the software, the datasets, and the process leading to
interpretable results that was used in a particular study. As much as possible,
publications should highlight that the code is
freely available in, for example, GitHub, and cite the DOI of the archived version
of the code that was used, together with any other
relevant information that may have been deposited. In our
experience, this openness substantially increases your chances of
getting the paper accepted for publication. On one hand, journal editors
and reviewers have the opportunity to reproduce your findings during the
manuscript review process, increasing their confidence in your results. On
the other hand, once the paper is published, your work can be reproduced
by any member of the scientific community, which can increase citations
and foster opportunities for further discussion and collaboration. Also
one must keep in mind that the availability of a public repository with
the source code does not make the software open source \emph{per se}, as
it also needs to have an appropriate license
(\url{http://opensource.org/licenses/}).
